A Comparision of Bootstrap Methods

### 2022-12-01 project/PaperTemplate/paper.Rmd
Added second part of simulation

  # find studentized
  t_q <- unname(quantile(boot_t_stat$t_stat, c(0.025, 0.975)))
  lower_q <- t_q[1]
  upper_q <- t_q[2]
  t_interval <- c(sample_mean - (upper_q*sample_se), sample_mean - (lower_q*sample_se))
  output <- list(standard_interval, percentile_interval, bc_interval, bca_interval, t_interval)
  names(output) <- c("Standard Interval", "Percentile Interval", "BC Interval", "BCa Interval", "Studentized Interval")
  output
}

@@

```{r}
set.seed(495)
#OUTPUT1 <- findCIs(values, 2000)
#OUTPUT1
```

>>>>

  # find studentized
  t_q <- unname(quantile(boot_t_stat$t_stat, c(0.025, 0.975)))
  lower_q <- t_q[1]
  upper_q <- t_q[2]
  t_interval <- c(sample_mean - (upper_q*sample_se), sample_mean - (lower_q*sample_se))

  output <- list(standard_interval, percentile_interval, bc_interval, bca_interval, t_interval)
  names(output) <- c("Standard Interval", "Percentile Interval", "BC Interval", "BCa Interval", "Studentized Interval")
  output
}

@@

```{r}
set.seed(495)
simulation_reps <- 30
trueparameter <- 4
n <- 100

ci <- matrix(nrow = simulation_reps, ncol = 5)

for (i in 1:simulation_reps){
  #X <- rnorm(n, trueparameter, 3)
  X <- rgamma(n, shape = 1, scale = 4)
  values <- data.frame(X)
  output <- findCIs(values, 2000)
  ci[i, 1] <- trueparameter >= output$`Standard Interval`[1] & trueparameter <= output$`Standard Interval`[2]
  ci[i, 2] <- trueparameter >= output$`Percentile Interval`[1] & trueparameter <= output$`Percentile Interval`[2]
  ci[i, 3] <- trueparameter >= output$`BC Interval`[1] & trueparameter <= output$`BC Interval`[2]
  ci[i, 4] <- trueparameter >= output$`BCa Interval`[1] & trueparameter <= output$`BCa Interval`[2]
  ci[i, 5] <- trueparameter >= output$`Studentized Interval`[1] & trueparameter <= output$`Studentized Interval`[2]

}

#ci <- as.data.frame(ci) %>%
#  rename("Standard Interval" = V1, "Percentile Interval" = V2, "BC Interval" = V3, "BCa Interval" = V4, "Studentized Interval" = V5)

output

ci_prop <- colSums(ci)/simulation_reps
ci_prop

```{r}
Y <- rgamma(5, shape = 8, scale = 2)
Y
